### 2018-12-10 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/abstract.tex
Initial version of the abstract.

\documentclass[12pt,a4paper]{article}
\usepackage{authblk}

\title{Solving Combinatorial Puzzles with Parallel Evolutionary Algorithms}

\author{Todor Balabanov}
\author{Stoyan Ivanov}
\author{Rumen Ketipov}

\affil{Institute of Information and Communication Technologies,
Bulgarian Academy of Sciences,
acad. G. Bonchev Str, Block 2, 1113 Sofia, Bulgaria,
todorb@iinf.bas.bg}

% Todor Balabanov todorb@iinf.bas.bg
% Stoyan Ivanov et_idea@abv.bg 
% Rumen Ketipov rnketipov@gmail.com

\date{December 10, 2018}

\begin{document}

\maketitle

ABSTRACT \\

Rubik's cube is the most popular combinatorial puzzle. It is well known that solutions of the combinatorial problems are generally hard to find. If 90 degree clockwise rotations of the cube's sides are taken as operations it will give a minimal cube's grammar. By building formal grammar sentences with the usage of the six operations ([L]eft, [R]ight, [T]op, [D]own, [F]ront, [B]ack) all cube's permutations can be achieved. In an evolutionary algorithms (like genetic algorithms for example) set of formal grammar sentences can be represented as population individuals. Single cut point crossover can be efficiently applied when population individuals are strings. Changing randomly selected operation with another randomly selected operation can be used as efficient mutation operator. The most important part of such global optimization is the fitness function. For better individuals fitness value evaluation a combination between Euclidean and Hausdorff distances is proposed in this research. The experiments in this research are done as parallel program written in C++ and Open MPI.

\end{document}

### 2018-12-18 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/abstract.tex
Abstract for second paper was added.

\documentclass[12pt,a4paper]{article}

\title{Alternatives for Neighborhood Function in Kohonen Maps}

\author{Iliyan Zankinski, Kolyu Kolev, Todor Balabanov}

% Iliyan Zankinski iliyan@hsi.iccs.bas.bg
% Kolyu Kolev kkolev@iit.bas.bg 
% Todor Balabanov todorb@iinf.bas.bg

% \affil{Institute of Information and Communication Technologies,
% Bulgarian Academy of Sciences,
% acad. G. Bonchev Str, Block 2, 1113 Sofia, Bulgaria,
% todorb@iinf.bas.bg}

\date{\empty}

\begin{document} 
\maketitle

In the field of the artificial intelligence artificial neural networks are one of the most researched topics. Multilayer perceptron has a reputation for the most used type of artificial neural network, but other other types, as Kohonen maps, are also very interesting. Proposed by Teuvo Kohonen in the 1980s, self-organizing maps have application in meteorology, oceanography, project prioritization and selection, seismic facies analysis for oil and gas exploration, failure mode and effects analysis, creation of artwork and many other areas. Self-organizing maps are very useful for visualization by data dimensions reduction. Unsupervised competitive learning is used in self-organizing maps and the basic idea is the net to classify input data in predefined number of clusters. When the net is with smaller number of nodes it achieve results similar to K-means clustering. One of the components in the self-organizing maps is the neighborhood function. It gives the distance between the neuron one neuron and other neuron in particular step. The simplest form of a neighborhood function is 1 for the closest nodes and 0 for all other, but the most used neighborhood function is a Gaussian function. In this research fading cosine and exponential regulated cosine functions are proposed as alternatives for neighborhood function.

\end{document}

### 2018-12-20 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/abstract.tex
Second talk abstract with final version.

@@
 
-% \affil{Institute of Information and Communication Technologies,
-% Bulgarian Academy of Sciences,
-% acad. G. Bonchev Str, Block 2, 1113 Sofia, Bulgaria,
-% todorb@iinf.bas.bg}
+% Institute of Information and Communication Technologies
+% Bulgarian Academy of Sciences
+% acad. G. Bonchev Str, Block 2, 1113 Sofia, Bulgaria
+% todorb@iinf.bas.bg
 
@@
 In the field of the artificial intelligence artificial neural networks are one of the most researched topics.
-Multilayer perceptron has a reputation for the most used type of artificial neural network, but other other types, as Kohonen maps, are also very interesting.
+Multilayer perceptron has a reputation for the most used type of artificial neural network, but other types such as Kohonen maps, are also very interesting.
 Proposed by Teuvo Kohonen in the 1980s, self-organizing maps have application in meteorology, oceanography, project prioritization and selection, seismic facies analysis for oil and gas exploration, failure mode and effects analysis, creation of artwork and many other areas.
@@
 Unsupervised competitive learning is used in self-organizing maps and the basic idea is the net to classify input data in predefined number of clusters.
-When the net is with smaller number of nodes it achieve results similar to K-means clustering.
+When the net has fewer nodes it achieve results similar to K-means clustering.
 One of the components in the self-organizing maps is the neighborhood function.
-It gives the distance between the neuron one neuron and other neuron in particular step.
-The simplest form of a neighborhood function is 1 for the closest nodes and 0 for all other, but the most used neighborhood function is a Gaussian function.
+It gives the distance between one neuron and other neurons in each step.
+The simplest form of a neighborhood function gives 1 for the closest nodes and 0 for all other, but the most used neighborhood function is a Gaussian function.
 In this research fading cosine and exponential regulated cosine functions are proposed as alternatives for neighborhood function.

### 2019-01-01 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Paper template was added.

--- 2018-12-10 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/abstract.tex
@@
-\documentclass[12pt,a4paper]{article}
-\usepackage{authblk}
+\documentclass[runningheads]{llncs}
 
-\title{Solving Combinatorial Puzzles with Parallel Evolutionary Algorithms}
-
-\author{Todor Balabanov}
-\author{Stoyan Ivanov}
-\author{Rumen Ketipov}
-
-\affil{Institute of Information and Communication Technologies,
-Bulgarian Academy of Sciences,
-acad. G. Bonchev Str, Block 2, 1113 Sofia, Bulgaria,
-todorb@iinf.bas.bg}
-
-% Todor Balabanov todorb@iinf.bas.bg
-% Stoyan Ivanov et_idea@abv.bg 
-% Rumen Ketipov rnketipov@gmail.com
-
-\date{December 10, 2018}
+\usepackage{graphicx}
+\usepackage{hyperref,xcolor}
+\renewcommand\UrlFont{\color{blue}\rmfamily}
 
@@
 
+\title{Solving Combinatorial Puzzles with Parallel Evolutionary Algorithms \thanks{This work was supported by a private funding of Velbazhd Software LLC.}}
+\titlerunning{Solving Puzzles with PEA}
+
+\author{Todor Balabanov\orcidID{0000-0003-3139-069X} \and
+Stoyan Ivanov \and
+Rumen Ketipov}
+\authorrunning{T. Balabanov et al.}
+
+\institute{Institute of Information and Communication Technologies \\
+Bulgarian Academy of Sciences \\
+acad. G. Bonchev Str, Block 2, 1113 Sofia, Bulgaria \\
+\email{todorb@iinf.bas.bg} \\
+\url{http://iict.bas.bg/}}
+
 \maketitle
 
-ABSTRACT \\
-
+\begin{abstract}
 Rubik's cube is the most popular combinatorial puzzle.
@@
 
+\keywords{Distributed evolutionary algorithms \and Combinatorial puzzles \and Integer optimization.}
+\end{abstract}
+
+\section{First Section}
+
+\subsection{A Subsection Sample}
+
+\subsubsection{Sample Heading (Third Level)}
+
+\paragraph{Sample Heading (Fourth Level)}
+
+\cite{ref_author1}
+\cite{ref_author2}
+\cite{ref_author3,ref_author4}
+
+\begin{thebibliography}{8}
+\bibitem{ref_author1}
+Family, N.: Article title. Journal \textbf{x}(y), pp--pp (yyyy)
+
+\bibitem{ref_author2}
+Family, N.: Article title. Journal \textbf{x}(y), pp--pp (yyyy)
+
+\bibitem{ref_author3}
+Family, N.: Article title. Journal \textbf{x}(y), pp--pp (yyyy)
+
+\bibitem{ref_author4}
+Family, N.: Article title. Journal \textbf{x}(y), pp--pp (yyyy)
+\end{thebibliography}
 \end{document}

### 2019-01-12 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Small part of the introduction section was added.

@@
 
-\section{First Section}
+\section{Introduction}
+
+A parallel implementation of a genetic algorithm based solver of the Rubik's cube was implemented by Balabanov in \cite{balabanov01} and it was presented in \cite{balabanov02}.
+Rubik's cube was invented and introduced by Erno Rubik in the 70s of the 20th century.
+After its creation the cube became the most popular combinatorial puzzle all over the world.
+In its original version it has 3x3x3 cubical segments.
 
@@
 
-\cite{ref_author1}
-\cite{ref_author2}
+\section{Conclusions}
+
 \cite{ref_author3,ref_author4}
@@
 \begin{thebibliography}{8}
-\bibitem{ref_author1}
-Family, N.: Article title. Journal \textbf{x}(y), pp--pp (yyyy)
-
-\bibitem{ref_author2}
-Family, N.: Article title. Journal \textbf{x}(y), pp--pp (yyyy)
+\bibitem{balabanov01}
+MPI Parallel Implementation of Genetic Algorithm Based Rubik’s Cube Solver, \url{http://github.com/TodorBalabanov/RubiksCubeGeneticAlgorithmsSolver}. Last accessed 12 Jan 2019
+\bibitem{balabanov02}
+Balabanov, T., Zankinski, I., Barova, M.: Strategy for Individuals Distribution by Incident Nodes Participation in Star Topology of Distributed Evolutionary Algorithms.
+Cybernetics and Information Technologies \textbf{16}(1), 80--88 (2016)
 

### 2019-01-14 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Initial version of the introduction was written.

@@
 Bulgarian Academy of Sciences \\
-acad. G. Bonchev Str, Block 2, 1113 Sofia, Bulgaria \\
+acad. Georgi Bonchev Str., Block 2, 1113 Sofia, Bulgaria \\
 \email{todorb@iinf.bas.bg} \\
@@
 In its original version it has 3x3x3 cubical segments.
+There are stickers in six different colors on each subcube square of the exposed sides.
+Each of the six planes (3x3x1) can be rotated in 90, 180, 270 or 360 degrees, relative to the other part of the puzzle.
+In the original initial state all sides of the cube are in single color.
+Scumbling of the puzzle is done by many random rotations of the (3x3x1) sides.
+The optimization task is to restore the cube in its original state.
+Such combinatorial optimization problem is quite difficult, because there are billions of combinations.
+The real number of combinations is $4.3252*10^{19}$ \cite{korf01} and all of them can be reached from any starting combination.
+The puzzle is successfully resolved when a sequence of moves is applied such that all subcubes are matched to each other by their color on each side of the cube.
+By estimation in \cite{korf01}, resolutions sequences variate from 50 to 100 moves when the is well scrambled.
 
-\subsection{A Subsection Sample}
+When there is an optimization problem with a sequence of commands it is a perfect candidate for evolutionary algorithms as optimizers.
+This research addresses the application of parallel genetic algorithms for Rubik's cube optimal or suboptimal solutions findings.
+The source code of the experiments is written in C++ with OpenMPI for parallel calculations and it can be found in a public source code repository \cite{balabanov01}.
+Modification of the evaluation function presented in \cite{balabanov02} is proposed by addition of Hausdorff distance component.
 
-\subsubsection{Sample Heading (Third Level)}
+The rest of this paper is organized as follows: Section 2 describes theoretical details.
+Section 3 presents the proposed modifications into a practical software example.
+Section 4 is devoted to some experiments and results.
+Finally, Section 5 concludes and presents some ideas for further research.
 
-\paragraph{Sample Heading (Fourth Level)}
+\section{Parallel Genetic Algorithms}
+
+\section{Modified Rubik's Cube Solver}
+
+\section{Experiments and Results}
 
 \section{Conclusions}
-
-\cite{ref_author3,ref_author4}
 
@@
 Cybernetics and Information Technologies \textbf{16}(1), 80--88 (2016)
-
-\bibitem{ref_author3}
-Family, N.: Article title. Journal \textbf{x}(y), pp--pp (yyyy)
-
-\bibitem{ref_author4}
-Family, N.: Article title. Journal \textbf{x}(y), pp--pp (yyyy)
+\bibitem{korf01}
+Korf, R.: Finding Optimal Solutions to Rubik’s Cube Using Pattern Databases. In: AAAI-98 Proceedings, pp. 700--705. AAAI Press, Menlo Park, CA, USA (1998)
 \end{thebibliography}

### 2019-01-24 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Some more text was added.

@@
 The source code of the experiments is written in C++ with OpenMPI for parallel calculations and it can be found in a public source code repository \cite{balabanov01}.
-Modification of the evaluation function presented in \cite{balabanov02} is proposed by addition of Hausdorff distance component.
+Modification of the evaluation function presented in \cite{balabanov02} is upgraded by addition of Hausdorff distance component.
 
@@
 \section{Modified Rubik's Cube Solver}
+
+The core of the optimization code is Rubik's cube representation into the computer memory.
+For the needs in this research the cube is presented as six (one for each side) two-dimensional (3x3) arrays.
+Values in these arrays are integer numbers which correspond to cube's colors.
+There are better ways for digital representation \cite{korf01}, but it is much more practical in this way from algorithmic aspect.
+
+Data structures are on first side of the modeling.
+On the second side are the algorithmic operations done over the data structures.
+The cube has six sides that is why the minimum number of operations over the cube is six.
+Six capital letters are used for 90 degrees clockwise rotations, as proposed in \cite{randall01,balabanov02}: \\
+\\
+T (Top) –90 degrees clockwise rotation of the top side; \\ 
+L (Left) –90 degrees clockwise rotation of the left side; \\ 
+B (Back) –90 degrees clockwise rotation of the back side; \\ 
+R (Right) –90 degrees clockwise rotation of the right side; \\ 
+F (Front) –90 degrees clockwise rotation of the front side; \\ 
+D (Down) –90 degrees clockwise rotation of the down side. \\
+
+This set of six operations is the minimal fully functional grammar for the Rubik's cube.
+Extended grammars are also possible, for example if counter-clockwise operators are included (+T, +L, +B, +R, +F, +D, –T, –L, –B, –R, –F, –D).
+Next level of extension is addition as number of turns (+1T, +2T, +3T, +1L, +2L, +3L, +1B, +2B, +3B, +1R, +2R, +3R, +1F, +2F, +3F, +1D,+2D, +3D, –1T, –2T, –3T, –1L, –2L, –3L, –1B, –2B, –3B, –1R, –2R, –3R, –1F, –2F, –3F, –1D, –2D, –3D) \cite{balabanov02}.
 
@@
 Korf, R.: Finding Optimal Solutions to Rubik’s Cube Using Pattern Databases. In: AAAI-98 Proceedings, pp. 700--705. AAAI Press, Menlo Park, CA, USA (1998)
+\bibitem{randall01}
+Randall, K.: Cilk - Efficient Multithreaded Computing. Doctor of Philosophy Thesis in Computer Science and Engineering, Massachusetts Institute of Technology, USA (1998) 
 \end{thebibliography}

### 2019-02-09 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Some more text were added.

@@
 \usepackage{graphicx}
+\usepackage{placeins}
 \usepackage{hyperref,xcolor}
@@
 The puzzle is successfully resolved when a sequence of moves is applied such that all subcubes are matched to each other by their color on each side of the cube.
-By estimation in \cite{korf01}, resolutions sequences variate from 50 to 100 moves when the is well scrambled.
+By estimation in \cite{korf01}, resolutions sequences variate from 50 to 100 moves when the cube is well scrambled.
 
@@
 
+With this clear idea for a formal Rubik's cube grammar it is neutral genetic algorithm individuals to be represented as formal grammar sentences with variable length.
+Each of the letters can appear at any position many times repeated in the chromosome.
+As it was appointed in \cite{korf01} the average expected length of the chromosomes can be between 50 and 100.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{fig01.png}
+\caption{Fitness value evaluation by combination between Euclidean and Hausdorff distance.} \label{fig01}
+\end{figure}
+\FloatBarrier
+
+Single cut point is selected as crossover population, but other options \cite{poli01} are also applicable.
+As mutation operator random change of a single instruction is selected.
+Selection is done by randomly selected parents, but elitism rule is applied.
+For the evaluation of the newly created individuals instructions encoded in the individual are applied over the scrambled cube.
+After that the state of the cube is compared with the target state (cube in the solved state).
+The listing in Fig.\ref{fig01} shows the proposed in this paper modification of fitness evaluation function.
+For each pairs of cube's sides Euclidean distance is calculated.
+After that according Hausdorff distance rules the maximum of the minimums is found.
+Evaluated fitness value is positive, because the Euclidean distance is calculated with positive integers (cube's colors are mapped to integers) and the Hausdorff distance is calculation of a maximum of the minimums.
+The puzzle is as better solved as the fitness value is smaller.
+
 \section{Experiments and Results}
 
+All experiments were done on a single processor desktop machine - Intel Core i5, 2.3 GHz, 2 Cores, 8GB RAM and Mac OS X 10.13.6, Apple LLVM version 9.1.0.
+For the parallel implementation Open MPI is used.
+
 \section{Conclusions}
+
+\cite{tashev01}
+
+\cite{alexandrov01}
+
+\cite{atanasova01}
 
@@
 Randall, K.: Cilk - Efficient Multithreaded Computing. Doctor of Philosophy Thesis in Computer Science and Engineering, Massachusetts Institute of Technology, USA (1998) 
+\bibitem{poli01}
+Poli, R., Kozak J.: Genetic Programming. In: Burke, EK., Kendall, G. (eds.) Search Methodologies, pp. 143--185. Springer US (2014)
+\bibitem{tashev01}
+Tashev, T., Hristov, H.: Modeling of synthesis of information processes with generalized nets. Cybernetics and Information Technologies, \textbf{3}(2), 92--104 (2003) 
+\bibitem{alexandrov01}
+Alexandrov, A.: AD HOC Kalman filter based fusion algorithm for real-time Wireless Sensor Data Integration. In: FQAS-2015 Proceedings, pp. 151--160. Springer, Heidelberg (2015)
+\bibitem{atanasova01}
+Atanasova T., Barova M.: Exploratory analysis of Time Series for hypothesize feature values. In: UniTech17 Proceedings,  \textbf{16}(2), 399--403 (2017)
 \end{thebibliography}

### 2019-02-10 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Some more text was added.

@@
 
+Genetic algorithms are global optimization strategy inspired from the evolution process in the Biology theories.
+Place of the genetic algorithms and the genetic programming in the family of the metaheuristics is well presented in Fig.\ref{fig02}.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{fig02.png}
+\centering
+\caption{Euler diagram of the different classifications of metaheuristics.} \label{fig02}
+\end{figure}
+\FloatBarrier
+
+Solutions of a particular problem are represented as vectors of values into the solution space.
+All selected solution vectors are the population of the algorithm.
+The most common way of initial population establishment is by generation of random vectors.
+Each new generation appears in the population after recombination of selected individuals.
+In genetic algorithms recombination is done by two consequent operators - crossover and mutation.
+Which individuals to participate in the recombination process is decided by application of selection operator.
+It is very common during selection process elitism rule to be applied.
+Elitism means that some percent of the best found solutions survive to the real end of the optimization process.
+Because such optimization procedure as implemented in the genetic algorithms is iterative, stopping criteria is needed.
+The most used stopping criteria is initially given number of genetic algorithm generations.
+
+Genetic algorithms are the base of the genetic programming which is used in this research.
+Each element of the solution vector actually is an operation applied over the state of the Rubik's cube.
+Ordered set of such instructions is actually an algorithmic program.
+Because there is no direct intermediate relation between the individuals in a particular population genetic algorithms are perfect for implementation in parallel computing or distributed computing.
+Population of the genetic algorithm can be easily divided is many sub-population and it can be distributed on many processors/cores or even heterogeneous computers in a cluster.
+Separation of the global population is the preferred approach, but in cases where only the fitness value calculation is time consuming population is kept in the central processor/computer and only fitness value calculation is sent to the other contributing processors/computers.
+
+When sub-populations distribution calculation scheme is selected some strategy for individual migration should be applied \cite{balabanov02}.
+Migration between different islands is needed in order best found solutions to be available in some or in all sub-populations.
+When the implementation of the calculation is organized as donated distributed computing project in the inclusion of a new remote contributing computer fresh subset of the global population can be supplied.
+With such strategy solutions space is much better investigated.
+
 \section{Modified Rubik's Cube Solver}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{fig01.png}
+\includegraphics[width=0.75\textwidth]{fig01.png}
+\centering
 \caption{Fitness value evaluation by combination between Euclidean and Hausdorff distance.} \label{fig01}
@@
 
-\cite{tashev01}
+The experiments clearly show that the addition of Hausdorff distance component improves the performance of the genetic algorithm.
+Calculation of the Hausdorff distance is a little bit slower than the calculation of the Euclidean distance, but better solution fitness estimation generally leads to genetic algorithm convergence improvement.
+Investigation in the field of the soft computing can be done for the proposed fitness value evaluation as it was done in \cite{angelova01}.
 
-\cite{alexandrov01}
-
-\cite{atanasova01}
+As further research it will be interesting evaluation of the fitness value to be additionally filtered with Kalman filter \cite{alexandrov01} for example.
+The other interesting direction would be imvolwment of the artificial neural networks such as \cite{tashev01,atanasova01} for preliminary solutions evaluation.
 
@@
 \bibitem{balabanov01}
-MPI Parallel Implementation of Genetic Algorithm Based Rubik’s Cube Solver, \url{http://github.com/TodorBalabanov/RubiksCubeGeneticAlgorithmsSolver}. Last accessed 12 Jan 2019
+MPI Parallel Implementation of Genetic Algorithm Based Rubik’s Cube Solver, \url{http://github.com/TodorBalabanov/RubiksCubeGeneticAlgorithmsSolver}. Last accessed 10 Feb 2019
 \bibitem{balabanov02}
@@
 Poli, R., Kozak J.: Genetic Programming. In: Burke, EK., Kendall, G. (eds.) Search Methodologies, pp. 143--185. Springer US (2014)
+\bibitem{angelova01}
+Angelova, V.: Investigations in the Area of Soft Computing Targeted State of the Art Report. Cybernetics and Information Technologies \textbf{9}(1), 18--24 (2009)
+\bibitem{alexandrov01}
+Alexandrov, A.: AD HOC Kalman filter based fusion algorithm for real-time Wireless Sensor Data Integration. In: FQAS-2015 Proceedings, pp. 151--160. Springer, Heidelberg (2015)
 \bibitem{tashev01}
 Tashev, T., Hristov, H.: Modeling of synthesis of information processes with generalized nets. Cybernetics and Information Technologies, \textbf{3}(2), 92--104 (2003) 
-\bibitem{alexandrov01}
-Alexandrov, A.: AD HOC Kalman filter based fusion algorithm for real-time Wireless Sensor Data Integration. In: FQAS-2015 Proceedings, pp. 151--160. Springer, Heidelberg (2015)
 \bibitem{atanasova01}

### 2019-02-13 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Initila version of the full text paper.

@@
 
+\begin{figure}
+\includegraphics[width=0.75\textwidth]{fig03.png}
+\centering
+\caption{Algorihtm convergence with star topology.} \label{fig03}
+\end{figure}
+\FloatBarrier
+
+Experiments are done in two groups with 30 independent runs for each.
+The source code originally is divided for test with star topology and incident nodes participation as migration strategies.
+That is why there are two groups of experiments.
+Each experiment compares pure Euclidean distance implementation and the proposed Hausdorff distance modification.
+
+\begin{figure}
+\includegraphics[width=0.75\textwidth]{fig04.png}
+\centering
+\caption{Algorihtm convergence with incident nodes participation.} \label{fig04}
+\end{figure}
+\FloatBarrier
+
+Fig.\ref{fig03} shows that when star topology is used the advantage of Hausdorff modification is not so big, but as it is shown in Fig.\ref{fig04} when incident nodes participation is used the proposed modification leads to convergence seep-up.
+
 \section{Conclusions}
 
-The experiments clearly show that the addition of Hausdorff distance component improves the performance of the genetic algorithm.
+The experiments show that the addition of Hausdorff distance component improves the performance of the genetic algorithm.
 Calculation of the Hausdorff distance is a little bit slower than the calculation of the Euclidean distance, but better solution fitness estimation generally leads to genetic algorithm convergence improvement.

### 2019-02-16 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/paper.tex
Paper frame was created.

--- 2019-02-09 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
@@
 
-\title{Solving Combinatorial Puzzles with Parallel Evolutionary Algorithms \thanks{This work was supported by a private funding of Velbazhd Software LLC.}}
-\titlerunning{Solving Puzzles with PEA}
+\title{Alternatives for Neighborhood Function in Kohonen Maps \thanks{This work was supported by a private funding of Velbazhd Software LLC.}}
+\titlerunning{Neighborhood in SOM}
 
-\author{Todor Balabanov\orcidID{0000-0003-3139-069X} \and
-Stoyan Ivanov \and
-Rumen Ketipov}
-\authorrunning{T. Balabanov et al.}
+\author{Iliyan Zankinski \and
+Kolyu Kolev \and
+Todor Balabanov\orcidID{0000-0003-3139-069X}}
+\authorrunning{I. Zankinski et al.}
 
@@
 acad. Georgi Bonchev Str., Block 2, 1113 Sofia, Bulgaria \\
-\email{todorb@iinf.bas.bg} \\
+\email{iliyan@hsi.iccs.bas.bg} \\
 \url{http://iict.bas.bg/}}
@@
 \begin{abstract}
-Rubik's cube is the most popular combinatorial puzzle.
-It is well known that solutions of the combinatorial problems are generally hard to find.
-If 90 degree clockwise rotations of the cube's sides are taken as operations it will give a minimal cube's grammar.
-By building formal grammar sentences with the usage of the six operations ([L]eft, [R]ight, [T]op, [D]own, [F]ront, [B]ack) all cube's permutations can be achieved.
-In an evolutionary algorithms (like genetic algorithms for example) set of formal grammar sentences can be represented as population individuals.
-Single cut point crossover can be efficiently applied when population individuals are strings.
-Changing randomly selected operation with another randomly selected operation can be used as efficient mutation operator.
-The most important part of such global optimization is the fitness function.
-For better individuals fitness value evaluation a combination between Euclidean and Hausdorff distances is proposed in this research.
-The experiments in this research are done as parallel program written in C++ and Open MPI.
+In the field of the artificial intelligence artificial neural networks are one of the most researched topics.
+Multilayer perceptron has a reputation for the most used type of artificial neural network, but other types such as Kohonen maps, are also very interesting.
+Proposed by Teuvo Kohonen in the 1980s, self-organizing maps have application in meteorology, oceanography, project prioritization and selection, seismic facies analysis for oil and gas exploration, failure mode and effects analysis, creation of artwork and many other areas.
+Self-organizing maps are very useful for visualization by data dimensions reduction.
+Unsupervised competitive learning is used in self-organizing maps and the basic idea is the net to classify input data in predefined number of clusters.
+When the net has fewer nodes it achieve results similar to K-means clustering.
+One of the components in the self-organizing maps is the neighborhood function.
+It gives the distance between one neuron and other neurons in each step.
+The simplest form of a neighborhood function gives 1 for the closest nodes and 0 for all other, but the most used neighborhood function is a Gaussian function.
+In this research fading cosine and exponential regulated cosine functions are proposed as alternatives for neighborhood function.
 
-\keywords{Distributed evolutionary algorithms \and Combinatorial puzzles \and Integer optimization.}
+\keywords{Artificial neural networks\and Self-organizing maps \and Neighborhood functions.}
 \end{abstract}
@@
 
-A parallel implementation of a genetic algorithm based solver of the Rubik's cube was implemented by Balabanov in \cite{balabanov01} and it was presented in \cite{balabanov02}.
-Rubik's cube was invented and introduced by Erno Rubik in the 70s of the 20th century.
-After its creation the cube became the most popular combinatorial puzzle all over the world.
-In its original version it has 3x3x3 cubical segments.
-There are stickers in six different colors on each subcube square of the exposed sides.
-Each of the six planes (3x3x1) can be rotated in 90, 180, 270 or 360 degrees, relative to the other part of the puzzle.
-In the original initial state all sides of the cube are in single color.
-Scumbling of the puzzle is done by many random rotations of the (3x3x1) sides.
-The optimization task is to restore the cube in its original state.
-Such combinatorial optimization problem is quite difficult, because there are billions of combinations.
-The real number of combinations is $4.3252*10^{19}$ \cite{korf01} and all of them can be reached from any starting combination.
-The puzzle is successfully resolved when a sequence of moves is applied such that all subcubes are matched to each other by their color on each side of the cube.
-By estimation in \cite{korf01}, resolutions sequences variate from 50 to 100 moves when the cube is well scrambled.
-
-When there is an optimization problem with a sequence of commands it is a perfect candidate for evolutionary algorithms as optimizers.
-This research addresses the application of parallel genetic algorithms for Rubik's cube optimal or suboptimal solutions findings.
-The source code of the experiments is written in C++ with OpenMPI for parallel calculations and it can be found in a public source code repository \cite{balabanov01}.
-Modification of the evaluation function presented in \cite{balabanov02} is upgraded by addition of Hausdorff distance component.
-
-The rest of this paper is organized as follows: Section 2 describes theoretical details.
-Section 3 presents the proposed modifications into a practical software example.
-Section 4 is devoted to some experiments and results.
-Finally, Section 5 concludes and presents some ideas for further research.
-
-\section{Parallel Genetic Algorithms}
-
-\section{Modified Rubik's Cube Solver}
-
-The core of the optimization code is Rubik's cube representation into the computer memory.
-For the needs in this research the cube is presented as six (one for each side) two-dimensional (3x3) arrays.
-Values in these arrays are integer numbers which correspond to cube's colors.
-There are better ways for digital representation \cite{korf01}, but it is much more practical in this way from algorithmic aspect.
-
-Data structures are on first side of the modeling.
-On the second side are the algorithmic operations done over the data structures.
-The cube has six sides that is why the minimum number of operations over the cube is six.
-Six capital letters are used for 90 degrees clockwise rotations, as proposed in \cite{randall01,balabanov02}: \\
-\\
-T (Top) –90 degrees clockwise rotation of the top side; \\ 
-L (Left) –90 degrees clockwise rotation of the left side; \\ 
-B (Back) –90 degrees clockwise rotation of the back side; \\ 
-R (Right) –90 degrees clockwise rotation of the right side; \\ 
-F (Front) –90 degrees clockwise rotation of the front side; \\ 
-D (Down) –90 degrees clockwise rotation of the down side. \\
-
-This set of six operations is the minimal fully functional grammar for the Rubik's cube.
-Extended grammars are also possible, for example if counter-clockwise operators are included (+T, +L, +B, +R, +F, +D, –T, –L, –B, –R, –F, –D).
-Next level of extension is addition as number of turns (+1T, +2T, +3T, +1L, +2L, +3L, +1B, +2B, +3B, +1R, +2R, +3R, +1F, +2F, +3F, +1D,+2D, +3D, –1T, –2T, –3T, –1L, –2L, –3L, –1B, –2B, –3B, –1R, –2R, –3R, –1F, –2F, –3F, –1D, –2D, –3D) \cite{balabanov02}.
-
-With this clear idea for a formal Rubik's cube grammar it is neutral genetic algorithm individuals to be represented as formal grammar sentences with variable length.
-Each of the letters can appear at any position many times repeated in the chromosome.
-As it was appointed in \cite{korf01} the average expected length of the chromosomes can be between 50 and 100.
-
-\begin{figure}
-\includegraphics[width=\textwidth]{fig01.png}
-\caption{Fitness value evaluation by combination between Euclidean and Hausdorff distance.} \label{fig01}
-\end{figure}
-\FloatBarrier
-
-Single cut point is selected as crossover population, but other options \cite{poli01} are also applicable.
-As mutation operator random change of a single instruction is selected.
-Selection is done by randomly selected parents, but elitism rule is applied.
-For the evaluation of the newly created individuals instructions encoded in the individual are applied over the scrambled cube.
-After that the state of the cube is compared with the target state (cube in the solved state).
-The listing in Fig.\ref{fig01} shows the proposed in this paper modification of fitness evaluation function.
-For each pairs of cube's sides Euclidean distance is calculated.
-After that according Hausdorff distance rules the maximum of the minimums is found.
-Evaluated fitness value is positive, because the Euclidean distance is calculated with positive integers (cube's colors are mapped to integers) and the Hausdorff distance is calculation of a maximum of the minimums.
-The puzzle is as better solved as the fitness value is smaller.
-
 \section{Experiments and Results}
@@
 All experiments were done on a single processor desktop machine - Intel Core i5, 2.3 GHz, 2 Cores, 8GB RAM and Mac OS X 10.13.6, Apple LLVM version 9.1.0.
-For the parallel implementation Open MPI is used.
 
@@
 
-\cite{tashev01}
-
-\cite{alexandrov01}
-
-\cite{atanasova01}
-
 \begin{thebibliography}{8}
-\bibitem{balabanov01}
-MPI Parallel Implementation of Genetic Algorithm Based Rubik’s Cube Solver, \url{http://github.com/TodorBalabanov/RubiksCubeGeneticAlgorithmsSolver}. Last accessed 12 Jan 2019
-\bibitem{balabanov02}
-Balabanov, T., Zankinski, I., Barova, M.: Strategy for Individuals Distribution by Incident Nodes Participation in Star Topology of Distributed Evolutionary Algorithms.
-Cybernetics and Information Technologies \textbf{16}(1), 80--88 (2016)
-\bibitem{korf01}
-Korf, R.: Finding Optimal Solutions to Rubik’s Cube Using Pattern Databases. In: AAAI-98 Proceedings, pp. 700--705. AAAI Press, Menlo Park, CA, USA (1998)
-\bibitem{randall01}
-Randall, K.: Cilk - Efficient Multithreaded Computing. Doctor of Philosophy Thesis in Computer Science and Engineering, Massachusetts Institute of Technology, USA (1998) 
-\bibitem{poli01}
-Poli, R., Kozak J.: Genetic Programming. In: Burke, EK., Kendall, G. (eds.) Search Methodologies, pp. 143--185. Springer US (2014)
+\bibitem{angelova01}
+Angelova, V.: Investigations in the Area of Soft Computing Targeted State of the Art Report. Cybernetics and Information Technologies \textbf{9}(1), 18--24 (2009)
+\bibitem{alexandrov01}
+Alexandrov, A.: AD HOC Kalman filter based fusion algorithm for real-time Wireless Sensor Data Integration. In: FQAS-2015 Proceedings, pp. 151--160. Springer, Heidelberg (2015)
 \bibitem{tashev01}
 Tashev, T., Hristov, H.: Modeling of synthesis of information processes with generalized nets. Cybernetics and Information Technologies, \textbf{3}(2), 92--104 (2003) 
-\bibitem{alexandrov01}
-Alexandrov, A.: AD HOC Kalman filter based fusion algorithm for real-time Wireless Sensor Data Integration. In: FQAS-2015 Proceedings, pp. 151--160. Springer, Heidelberg (2015)
 \bibitem{atanasova01}

### 2019-02-16 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/paper.tex
Small fix of the abstract.

@@
 In the field of the artificial intelligence artificial neural networks are one of the most researched topics.
-Multilayer perceptron has a reputation for the most used type of artificial neural network, but other types such as Kohonen maps, are also very interesting.
+Multilayer perceptron has a reputation for the most used type of artificial neural network, but other types such as Kohonen maps, generalized nets\cite{tashev01} or combinations with Kalman filter\cite{alexandrov01} are also very interesting.
 Proposed by Teuvo Kohonen in the 1980s, self-organizing maps have application in meteorology, oceanography, project prioritization and selection, seismic facies analysis for oil and gas exploration, failure mode and effects analysis, creation of artwork and many other areas.
@@
 \begin{thebibliography}{8}
+\bibitem{tashev01}
+Tashev, T., Hristov, H.: Modeling of synthesis of information processes with generalized nets. Cybernetics and Information Technologies, \textbf{3}(2), 92--104 (2003) 
+\bibitem{alexandrov01}
+Alexandrov, A.: AD HOC Kalman filter based fusion algorithm for real-time Wireless Sensor Data Integration. In: FQAS-2015 Proceedings, pp. 151--160. Springer, Heidelberg (2015)
 \bibitem{angelova01}
 Angelova, V.: Investigations in the Area of Soft Computing Targeted State of the Art Report. Cybernetics and Information Technologies \textbf{9}(1), 18--24 (2009)
-\bibitem{alexandrov01}
-Alexandrov, A.: AD HOC Kalman filter based fusion algorithm for real-time Wireless Sensor Data Integration. In: FQAS-2015 Proceedings, pp. 151--160. Springer, Heidelberg (2015)
-\bibitem{tashev01}
-Tashev, T., Hristov, H.: Modeling of synthesis of information processes with generalized nets. Cybernetics and Information Technologies, \textbf{3}(2), 92--104 (2003) 
 \bibitem{atanasova01}

### 2019-02-16 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/paper.tex
Small part of the introduction was written.

@@
 
-\keywords{Artificial neural networks\and Self-organizing maps \and Neighborhood functions.}
+\keywords{Artificial neural networks \and Self-organizing maps \and Neighborhood functions.}
 \end{abstract}
@@
 \section{Introduction}
+
+Self-organizing maps or Kohonen Neural Networks (KNNs) are networks with unsupervised training.
+They are very useful in finding nonlinear dependencies when data are presented in very high dimensional spaces.
+The projection from the high-dimensional space is usually done in a rectangular lower-dimensional space.
+The main idea behind KNNs is the organization of unlabeled vectors with particular features in predefined number of groups called clusters.
 

### 2019-02-18 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/paper.tex
Another part of the introduction.

@@
 One of the components in the self-organizing maps is the neighborhood function.
-It gives the distance between one neuron and other neurons in each step.
+It gives scaling factor for the distance between one neuron and other neurons in each step.
 The simplest form of a neighborhood function gives 1 for the closest nodes and 0 for all other, but the most used neighborhood function is a Gaussian function.
@@
 The main idea behind KNNs is the organization of unlabeled vectors with particular features in predefined number of groups called clusters.
+Grid of the self-organizing map is a handy tool for convenient visualization which can reveal different features of the network.
+SOMs are attractive when there consist of two or more separate regions.
+The real goal is not to find a perfect clustering but get good idea of the cluster structure.
+
+\subsection{Clustering}
+
+Clustering means a separation of the data set in set of groups.
+In separation where each data sample belongs exactly to only one group it is called straight clustering.
+If each data sample has varying degree of membership to different groups it is called fuzzy clustering.
+
+Generally accepted concept of an optimal clustering is data set separation which minimizes the distance inside the cluster and maximizes the distance between the clusters.
+The most used form of distance measurement is the Euclidean norm.
+
+\subsection{SOM Training}
+
+The network consists of a grid (usually two dimensional) with units.
+The units are connected to adjacent units with a neighborhood relation.
+The amount of grid units, which usually varies from a few dozen up to several thousand, gives the accuracy and generalization possibilities of the KNN.
+The network forms an elastic mesh that folds
+as a cloud formed by the input data during training phase. Data samples lying near each other in the input space are mapped into nearby grid units.
+
+The network training is done iteratively.
+A data sample vector is randomly chosen from the input data set, as first step.
+As second step, distances between the selected vector and all the prototype vectors are computed.
+The best matching unit is the grid unit with prototype closest the selected vector.
+In the third step, the prototype vectors in the grid are updated.
+The best matching unit and its topological neighbors are moved closer to the input vector in the input space.
+
+\cite{vesanto01}
 
@@
 Alexandrov, A.: AD HOC Kalman filter based fusion algorithm for real-time Wireless Sensor Data Integration. In: FQAS-2015 Proceedings, pp. 151--160. Springer, Heidelberg (2015)
+\bibitem{vesanto01}
+Vesanto, J., Alhoniemi, E.: Clustering of the Self-Organizing Map. IEEE Transactions on Neural Networks, \textbf{11}(3), 586--600 (2000) 
 \bibitem{angelova01}

### 2019-02-20 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/paper.tex
Some of the main text was written.

@@
 \renewcommand\UrlFont{\color{blue}\rmfamily}
+\usepackage{amsmath}
 
@@
 In the third step, the prototype vectors in the grid are updated.
-The best matching unit and its topological neighbors are moved closer to the input vector in the input space.
+The best matching unit and its topological neighbors are moved closer to the input vector in the input space \cite{vesanto01}.
 
-\cite{vesanto01}
+\section{Neighborhood Function}
+
+The most used KNN's neighborhood function is the Gaussian function.
+In this research two alternative functions are proposed.
+The first function is fading cosine, which is shown in Fig.\ref{fig01}-Left.
+The second function is exponential regulated cosine, which is shown in FIg.\ref{fig01}-Right.
+
+\begin{figure}
+\includegraphics[width=1.0\textwidth]{fig01.png}
+\centering
+\caption{Left - Fading cosine neighborhood function. Right - Exponential regulated cosine neighborhood function.} \label{fig01}
+\end{figure}
+\FloatBarrier
+
+The idea for the both functions is to stress grid nodes down and up. The exponential regulated cosine Eq.\ref{equ02} gives smoother stress than the fading cosine Eq.\ref{equ01}.
+
+\begin{equation} \label{equ01}
+f(x) = 
+	\begin{cases} 
+		cos(x) \\
+		\frac{cos(x)}{|x|} \\
+	\end{cases}
+\end{equation}
+
+\begin{equation} \label{equ02}
+f(x) = \frac{cos(x)}{e^{|x|}}
+\end{equation}
 

### 2019-02-20 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Some corrections were done by Rumen.

@@
 
-A parallel implementation of a genetic algorithm based solver of the Rubik's cube was implemented by Balabanov in \cite{balabanov01} and it was presented in \cite{balabanov02}.
+A parallel implementation of a genetic algorithm-based solver of the Rubik's cube was implemented by Balabanov in \cite{balabanov01} and it was presented in \cite{balabanov02}.
 Rubik's cube was invented and introduced by Erno Rubik in the 70s of the 20th century.
@@
 Scumbling of the puzzle is done by many random rotations of the (3x3x1) sides.
-The optimization task is to restore the cube in its original state.
-Such combinatorial optimization problem is quite difficult, because there are billions of combinations.
+The optimization task aims to restore the cube in its original state.
+Such combinatorial optimization problem is quite difficult because there are billions of combinations.
 The real number of combinations is $4.3252*10^{19}$ \cite{korf01} and all of them can be reached from any starting combination.
 The puzzle is successfully resolved when a sequence of moves is applied such that all subcubes are matched to each other by their color on each side of the cube.
-By estimation in \cite{korf01}, resolutions sequences variate from 50 to 100 moves when the cube is well scrambled.
+According to an estimation in \cite{korf01} resolutions sequences variate from 50 to 100 moves when the cube is well scrambled.
 
@@
 
-The rest of this paper is organized as follows: Section 2 describes theoretical details.
-Section 3 presents the proposed modifications into a practical software example.
-Section 4 is devoted to some experiments and results.
+The rest of this paper is organized as follows: Section 2 briefly describes theoretical details.
+Hence, section 3 presents the proposed modifications into a practical software example and section 4 is devoted to some experiments and results.
 Finally, Section 5 concludes and presents some ideas for further research.
@@
 Ordered set of such instructions is actually an algorithmic program.
-Because there is no direct intermediate relation between the individuals in a particular population genetic algorithms are perfect for implementation in parallel computing or distributed computing.
+Because there is no direct intermediate relation between the individuals in a particular population genetic algorithms are highly appropriate for implementation in parallel computing or distributed computing.
 Population of the genetic algorithm can be easily divided is many sub-population and it can be distributed on many processors/cores or even heterogeneous computers in a cluster.
-Separation of the global population is the preferred approach, but in cases where only the fitness value calculation is time consuming population is kept in the central processor/computer and only fitness value calculation is sent to the other contributing processors/computers.
+Separation of the global population is the preferred approach, but in cases where only the fitness value calculation is time consuming, population is kept in the central processor/computer and only fitness value calculation is sent to the other contributing processors/computers.
 
@@
 For each pairs of cube's sides Euclidean distance is calculated.
-After that according Hausdorff distance rules the maximum of the minimums is found.
-Evaluated fitness value is positive, because the Euclidean distance is calculated with positive integers (cube's colors are mapped to integers) and the Hausdorff distance is calculation of a maximum of the minimums.
+After that according to Hausdorff distance rules the maximum of the minimums is found.
+Evaluated fitness value is positive because the Euclidean distance is calculated with positive integers (cube's colors are mapped to integers) and the Hausdorff distance is a calculation of a maximum of the minimums.
 The puzzle is as better solved as the fitness value is smaller.
@@
 
-Fig.\ref{fig03} shows that when star topology is used the advantage of Hausdorff modification is not so big, but as it is shown in Fig.\ref{fig04} when incident nodes participation is used the proposed modification leads to convergence seep-up.
+Fig.\ref{fig03} shows that when star topology is used the advantage of Hausdorff modification is not so great, but as it is shown in Fig.\ref{fig04} when an incident nodes participation is used the proposed modification leads to convergence seep-up.
 
@@
 The experiments show that the addition of Hausdorff distance component improves the performance of the genetic algorithm.
-Calculation of the Hausdorff distance is a little bit slower than the calculation of the Euclidean distance, but better solution fitness estimation generally leads to genetic algorithm convergence improvement.
-Investigation in the field of the soft computing can be done for the proposed fitness value evaluation as it was done in \cite{angelova01}.
+A calculation of the Hausdorff distance is a little bit slower than the calculation of the Euclidean distance, but better solution fitness estimation generally leads to genetic algorithm convergence improvement.
+Further investigations in the field of the soft computing can be done for the proposed fitness value evaluation as it was done in \cite{angelova01}.
 
-As further research it will be interesting evaluation of the fitness value to be additionally filtered with Kalman filter \cite{alexandrov01} for example.
-The other interesting direction would be imvolwment of the artificial neural networks such as \cite{tashev01,atanasova01} for preliminary solutions evaluation.
+As further research it will be interesting an evaluation of the fitness value to be additionally filtered with Kalman filter \cite{alexandrov01}, for example.
+Another interesting direction would be an involvement of the artificial neural networks such as \cite{tashev01,atanasova01} for preliminary solutions evaluation.
 

### 2019-02-21 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/paper.tex
The proposed equations are given.
Small amount of text was added.

@@
 In the field of the artificial intelligence artificial neural networks are one of the most researched topics.
-Multilayer perceptron has a reputation for the most used type of artificial neural network, but other types such as Kohonen maps, generalized nets\cite{tashev01} or combinations with Kalman filter\cite{alexandrov01} are also very interesting.
+Multilayer perceptron has a reputation for the most used type of artificial neural network, but other types such as Kohonen maps, generalized nets\cite{tashev01} or combinations with Kalman filter\cite{alexandrov01,voort01} are also very interesting.
 Proposed by Teuvo Kohonen in the 1980s, self-organizing maps have application in meteorology, oceanography, project prioritization and selection, seismic facies analysis for oil and gas exploration, failure mode and effects analysis, creation of artwork and many other areas.
@@
 
-Self-organizing maps or Kohonen Neural Networks (KNNs) are networks with unsupervised training.
+Self-organizing maps or Kohonen Neural Networks (KNNs) are networks with unsupervised training \cite{schreck01}.
 They are very useful in finding nonlinear dependencies when data are presented in very high dimensional spaces.
 The projection from the high-dimensional space is usually done in a rectangular lower-dimensional space.
-The main idea behind KNNs is the organization of unlabeled vectors with particular features in predefined number of groups called clusters.
+The main idea behind KNNs is the organization of unlabeled vectors with particular features in predefined number of groups called clusters \cite{cottrell01}.
 Grid of the self-organizing map is a handy tool for convenient visualization which can reveal different features of the network.
@@
 
-The network consists of a grid (usually two dimensional) with units.
+The network consists of a grid (usually two dimensional \cite{wehrens01}) with units.
 The units are connected to adjacent units with a neighborhood relation.
@@
 	\begin{cases} 
-		cos(x) \\
-		\frac{cos(x)}{|x|} \\
+		cos(x) & +\pi/2 \geq x \leq -\pi/2 \\
+		\frac{cos(x)}{|x|} & -\pi/2 < x < \pi/2 \\
 	\end{cases}
@@
 
+The proposed neighbor functions give promising results as it is shown in the experimental section.
+Stressing the neighboring nodes down and up leads to better separation between the formed clusters.
+As further research it will be interesting the proposed neighborhood functions to be combined with different distance norms.
+In some problems Hausdorff distance can be used for example.
+
 \begin{thebibliography}{8}
+
 \bibitem{tashev01}
 Tashev, T., Hristov, H.: Modeling of synthesis of information processes with generalized nets. Cybernetics and Information Technologies, \textbf{3}(2), 92--104 (2003)
+
 \bibitem{alexandrov01}
 Alexandrov, A.: AD HOC Kalman filter based fusion algorithm for real-time Wireless Sensor Data Integration. In: FQAS-2015 Proceedings, pp. 151--160. Springer, Heidelberg (2015)
+
+\bibitem{voort01}
+van der Voort, M., Dougherty, M.,Watson, S.: Combining kohonen maps with arima time series models to forecast traffic flow.
+Transportation Research Part C: Emerging Technologies, \textbf{4}(5), 307--318 (1996)
+
+\bibitem{schreck01}
+Schreck, T., Bernard, J., Landesberger, T. von, Kohlhammer, J.: Visual Cluster Analysis of Trajectory Data with Interactive Kohonen Maps. Information Visualization, \textbf{8}(1), 14--29 (2009)
+
+\bibitem{cottrell01}
+Cottrell M., Letremy P., Roy E.: Analysing a contingency table with Kohonen maps: A factorial correspondence analysis.
+In: Mira J., Cabestany J., Prieto A.
+(eds) New Trends in Neural Computation.
+Lecture Notes in Computer Science, pp.
+305--311.
+Springer, Heidelberg (1993)
+
+\bibitem{wehrens01}
+Wehrens, R., Buydens, L.: Self- and Super-organizing Maps in R: The kohonen Package. Journal of statistical software, \textbf{21}(5), 1--19 (2007)
+
 \bibitem{vesanto01}
 Vesanto, J., Alhoniemi, E.: Clustering of the Self-Organizing Map. IEEE Transactions on Neural Networks, \textbf{11}(3), 586--600 (2000)
+
 \bibitem{angelova01}
 Angelova, V.: Investigations in the Area of Soft Computing Targeted State of the Art Report. Cybernetics and Information Technologies \textbf{9}(1), 18--24 (2009)
+
 \bibitem{atanasova01}
 Atanasova T., Barova M.: Exploratory analysis of Time Series for hypothesize feature values. In: UniTech17 Proceedings,  \textbf{16}(2), 399--403 (2017)
+
 \end{thebibliography}

### 2019-02-24 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/paper.tex
Small additions.

@@
 They are very useful in finding nonlinear dependencies when data are presented in very high dimensional spaces.
-The projection from the high-dimensional space is usually done in a rectangular lower-dimensional space.
+The projection from the high-dimensional space is usually done in a rectangular lower-dimensional space \cite{macq01}.
 The main idea behind KNNs is the organization of unlabeled vectors with particular features in predefined number of groups called clusters \cite{cottrell01}.
@@
 Generally accepted concept of an optimal clustering is data set separation which minimizes the distance inside the cluster and maximizes the distance between the clusters.
-The most used form of distance measurement is the Euclidean norm.
+The most used form of distance measurement is the Euclidean norm \cite{lozano01}.
 
@@
 The amount of grid units, which usually varies from a few dozen up to several thousand, gives the accuracy and generalization possibilities of the KNN.
-The network forms an elastic mesh that folds
-as a cloud formed by the input data during training phase. Data samples lying near each other in the input space are mapped into nearby grid units.
+The network forms an elastic mesh that folds as a cloud formed by the input data during training phase.
+Data samples lying near each other in the input space are mapped into nearby grid units.
 
@@
 In the third step, the prototype vectors in the grid are updated.
-The best matching unit and its topological neighbors are moved closer to the input vector in the input space \cite{vesanto01}.
+The best matching unit and its topological neighbors are moved closer to the input vector in the input space \cite{vesanto01,аmerijckx01}.
 
@@
 
+\bibitem{macq01}
+Macq, D., Verleysen, M., Jespers, P., Legat, J.D.: Analog implementation of a Kohonen map with on-chip learning. IEEE Transactions on Neural Networks, \textbf{4}(3), 456--461 (1993)
+
 \bibitem{cottrell01}
@@
 
+\bibitem{lozano01}
+Lozano, S., Guerrero, F., Onieva, L., Larraneta, J.: Kohonen maps for solving a class of location-allocation problems. European Journal of Operational Research, \textbf{108}(1), 106--117 (1998)
+
 \bibitem{wehrens01}
@@
 Vesanto, J., Alhoniemi, E.: Clustering of the Self-Organizing Map. IEEE Transactions on Neural Networks, \textbf{11}(3), 586--600 (2000)
+
+\bibitem{аmerijckx01}
+Amerijckx, C., Verleysen, M., Thissen, P., Legat, J.D.: Image compression by self-organized Kohonen map. IEEE Transactions on Neural Networks, \textbf{9}(3), 503--507 (1998)
 

### 2019-03-01 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/paper.tex
Initial version of the full text is available.

@@
 	\begin{cases} 
-		cos(x) & +\pi/2 \geq x \leq -\pi/2 \\
-		\frac{cos(x)}{|x|} & -\pi/2 < x < \pi/2 \\
+		cos(x) & -\pi/2 < x < \pi/2 \\
+		\frac{cos(x)}{|x|} & +\pi/2 \geq x \leq -\pi/2 \\
 	\end{cases}
@@
 
+\begin{figure}
+\includegraphics[width=1.0\textwidth]{fig03.png}
+\centering
+\caption{Rents and living area data set \cite{garriga01}.} \label{fig03}
+\end{figure}
+\FloatBarrier
+
+As experimental data set rents and living area (shown in Fig.\ref{fig03}) are taken from the open source project, which can be found at \cite{garriga01}.
+
+Experiments are done with Gausssian neighborhood function Fig.\ref{fig02}-Left, fading cosine neighborhood function Fig.\ref{fig02}-Center and exponential regulated cosine neighborhood function Fig.\ref{fig02}-Right.
+Results show that fading cosine function performs less effective than exponential regulated cosine, but exponential regulated cosine gives sharper clusters separation than the Gaussian function.
+
+\begin{figure}
+\includegraphics[width=1.0\textwidth]{fig02.png}
+\centering
+\caption{Left - Gausssian neighborhood function. Center - Fading cosine neighborhood function. Right - Exponential regulated cosine neighborhood function.} \label{fig02}
+\end{figure}
+\FloatBarrier
+
 \section{Conclusions}
@@
 In some problems Hausdorff distance can be used for example.
+Situations in time series \cite{atanasova01} are also interesting for classification with KNN and the capabilities of the soft computing \cite{angelova01}.
 
@@
 
-\bibitem{angelova01}
-Angelova, V.: Investigations in the Area of Soft Computing Targeted State of the Art Report. Cybernetics and Information Technologies \textbf{9}(1), 18--24 (2009)
+\bibitem{garriga01}
+Complete C implementation of the Kohonen Neural Network (SOM algorithm), \url{http://github.com/Coding-Sunday-Sofia/Kohonen}. Last accessed 01 Mar 2019
 
@@
 
+\bibitem{angelova01}
+Angelova, V.: Investigations in the Area of Soft Computing Targeted State of the Art Report. Cybernetics and Information Technologies \textbf{9}(1), 18--24 (2009)
+
 \end{thebibliography}

### 2019-03-07 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Some changes were done by Vera Angelova.

@@
 Elitism means that some percent of the best found solutions survive to the real end of the optimization process.
-Because such optimization procedure as implemented in the genetic algorithms is iterative, stopping criteria is needed.
+Because genetic algorithms based optimization is an iterative optimization a stopping criteria is needed.
 The most used stopping criteria is initially given number of genetic algorithm generations.
@@
 Because there is no direct intermediate relation between the individuals in a particular population genetic algorithms are highly appropriate for implementation in parallel computing or distributed computing.
-Population of the genetic algorithm can be easily divided is many sub-population and it can be distributed on many processors/cores or even heterogeneous computers in a cluster.
+Population of the genetic algorithm can be easily divided in many sub-population and it can be distributed on many processors/cores or even heterogeneous computers in a cluster.
 Separation of the global population is the preferred approach, but in cases where only the fitness value calculation is time consuming, population is kept in the central processor/computer and only fitness value calculation is sent to the other contributing processors/computers.
@@
 
-Data structures are on first side of the modeling.
+Data structures are the first side of the modeling proccess.
 On the second side are the algorithmic operations done over the data structures.
@@
 
-With this clear idea for a formal Rubik's cube grammar it is neutral genetic algorithm individuals to be represented as formal grammar sentences with variable length.
+With the presented ideas for a formal Rubik's cube grammar the neutral choice is genetic algorithm individuals to be represented as formal grammar sentences with variable length.
 Each of the letters can appear at any position many times repeated in the chromosome.

### 2019-05-30 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/paper.tex
Final version.

@@
 \renewcommand\UrlFont{\color{blue}\rmfamily}
+\usepackage{listings}
+\definecolor{very-light-gray}{gray}{0.95}
 
@@
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{fig02.png}
+\includegraphics[width=1.0\textwidth,height=0.65\textwidth]{fig02.png}
 \centering
@@
 \end{figure}
-\FloatBarrier
+%\FloatBarrier
 
@@
 Each experiment compares pure Euclidean distance implementation and the proposed Hausdorff distance modification.
+Parameters of the genetic algorithm are listed in Tab.
+\ref{tab01}.
+
+\begin{table}
+\caption{Genetic algorithm parameters.}
+\label{tab01}
+\begin{tabular}{p{6.9cm}p{4.4cm}}
+\hline\noalign{\smallskip}
+\textbf{Parameter} & \textbf{Value} \\
+\hline\noalign{\smallskip}
+generation gap & 0.93 \\
+crossover rate & 0.98 \\
+mutation rate & 0.01 \\
+maximum generations & 10000 \\
+number of individuals & 37 \\
+number of variables & floating \\
+inserted rate & 100 \% \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+\end{tabular}
+\end{table}
+\FloatBarrier
 
@@
 Fig.\ref{fig03} shows that when star topology is used the advantage of Hausdorff modification is not so great, but as it is shown in Fig.\ref{fig04} when an incident nodes participation is used the proposed modification leads to convergence seep-up.
+Calculation of a Euclidean distance between two cubes uses six calculations of the sides for the cube (Listing \ref{lst01}).
+In the case of Hausdorff distance there are six times more calls of a single Euclidean distance calculation (Listing \ref{lst02}).
+
+\begin{lstlisting}[caption={Euclidean distance.},label={lst01},backgroundcolor=\color{very-light-gray},frame={single}]
+double euclidean(const int side1[3][3], 
+                 const int side2[3][3]) const {
+  double distance = 0.0;
+
+  for(int i=0; i<3; i++) {
+    for(int j=0; j<3; j++) {
+      distance += (side1[i][j]-side2[i][j]) * 
+                  (side1[i][j]-side2[i][j]);
+    }
+  }
+
+  return sqrt(distance);
+}
+\end{lstlisting}
+\FloatBarrier
+
+\begin{lstlisting}[caption={Hausdorff distance.},label={lst02},backgroundcolor=\color{very-light-gray},frame={single}]
+double hausdorff(const RubiksCube &cube) const {
+  double min[] = {INT_MAX, INT_MAX, INT_MAX, 
+                  INT_MAX, INT_MAX, INT_MAX};
+
+  for(int s1=0; s1<6; s1++) {
+    for(int s2=0; s2<6; s2++) {
+      double distance = 
+      euclidean(*sides[s1], *(cube.sides)[s2]);
+
+      if(min[s1] > distance) {
+        min[s1] = distance;
+      }
+    }
+  }
+
+  double result = min[0];
+  for(int s1=0; s1<6; s1++) {
+    if(result < min[s1]) {
+      result = min[s1];
+    }
+  }
+
+  return(result);
+}
+\end{lstlisting}
+\FloatBarrier
 

### 2019-05-31 Alternatives-for-Neighborhood-Function-in-Kohonen-Maps/presentation.tex
Presentation was added.

\documentclass{beamer}

\mode<presentation> {
	\usetheme{Berlin}
}

\title[12th International Conference on Large-Scale Scientific Computations, June 10 - 14, 2019, Sozopol, Bulgaria]{
	Alternatives for Neighborhood Function in Kohonen Maps
}

\author{Iliyan Zankinski, Kolyu Kolev, Todor Balabanov}

\date{10-14.VI.2019}

\institute[IICT-BAS, LSSC'19] {
	Institute of Information and Communication Technologies \\ 
	Bulgarian Academy of Sciences \\
	\medskip
	\textit{iliyan@hsi.iccs.bas.bg}
}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Overview}
\tableofcontents
\end{frame}

\section{Introduction}

\begin{frame}
\center \huge{Introduction}
\end{frame}

\begin{frame}
\frametitle{Clustering}
\begin{itemize}
  \item Separation of the data set in set of groups
  \item Straight clustering - each data sample belongs exactly to only one group
  \item Fuzzy clustering - each data sample has varying degree of membership to different groups
\end{itemize}
Optimal clustering is data set separation which minimizes the distance inside the cluster and maximizes the distance between the clusters
\end{frame}

\begin{frame}
\frametitle{Self-Organizing Maps}
\begin{itemize}
  \item Proposed by Teuvo Kohonen in the 1980s
  \item Have application in meteorology, oceanography, project prioritization and selection, seismic facies analysis for oil and gas exploration, failure mode and effects analysis, creation of artwork and many other areas
  \item They are very useful for visualization by data dimensions reduction
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{SOM in General}
\begin{itemize}
  \item Unsupervised competitive learning is used
  \item Classify input data in predefined number of clusters
  \item When the net has fewer nodes it achieve results similar to K-means clustering
\end{itemize}
\end{frame}

\section{Neighborhood Function Proposition}

\begin{frame}
\center \huge{Neighborhood Function Proposition}
\end{frame}

\begin{frame}
\frametitle{SOM Training}
\begin{itemize}
  \item The network consists of a grid with units
  \item The units are connected to adjacent units with a neighborhood relation
  \item The network forms an elastic mesh
  \item Data samples lying near each other in the input space are mapped into nearby grid units
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Neighborhood Function}
\begin{itemize}
  \item It gives scaling factor for the distance between one neuron and other neurons in each step
  \item The simplest form of a neighborhood function gives 1 for the closest nodes and 0 for all other
  \item The most used neighborhood function is a Gaussian function
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Fading Cosine}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\linewidth]{fig01a}
\label{fig01a}
\end{figure}
\begin{equation} \label{equ01}
f(x) = 
	\begin{cases} 
		cos(x) & -\pi/2 < x < \pi/2 \\
		\frac{cos(x)}{|x|} & +\pi/2 \geq x \leq -\pi/2 \\
	\end{cases}
\end{equation}
\end{frame}

\begin{frame}
\frametitle{Exponential Regulated Cosine}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\linewidth]{fig01b}
\label{fig01b}
\end{figure}
\begin{equation} \label{equ02}
f(x) = \frac{cos(x)}{e^{|x|}}
\end{equation}
\end{frame}

\section{Experiments and Results}

\begin{frame}
\center \huge{Experiments and Results}
\end{frame}

\begin{frame}
\frametitle{Experimental Setup}
\begin{itemize}
  \item All experiments are done in C as a programming language
  \item Single processor desktop machine - Intel Core i5, 2.3 GHz, 2 Cores, 8GB RAM and Mac OS X 10.13.6, Apple LLVM version 9.1.0
  \item The source code is available at: 
  http://github.com/Coding-Sunday-Sofia/Kohonen
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Experimental Data}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.9\textwidth]{fig03}
  \label{fig03}
\end{figure}
Rents and living area data set
\end{frame}

\begin{frame}
\frametitle{Gausssian Test}
\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02a}
  \label{fig02a}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Fading Cosine Test}
\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02b}
  \label{fig02b}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Exponential Regulated Cosine Test}
\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02c}
  \label{fig02c}
\end{figure}
\end{frame}

\section{Conclusions}

\begin{frame}
\center \huge{Conclusions}
\end{frame}

\begin{frame}
\frametitle{Concluding Remarks}
\begin{itemize}
  \item The proposed neighbor functions give promising results
  \item Stressing the neighboring nodes down and up leads to better separation between the formed clusters
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Questions and Answers}
\center \huge{Thank you for the attention!}
\end{frame}

\end{document}

### 2019-06-01 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/presentation.tex
Presentation template was added.

\documentclass{beamer}

\mode<presentation> {
	\usetheme{Berlin}
}

\title[12th International Conference on Large-Scale Scientific Computations, June 10 - 14, 2019, Sozopol, Bulgaria]{
	Solving Combinatorial Puzzles with Parallel Evolutionary Algorithms
}

\author{Todor Balabanov, Stoyan Ivanov, Rumen Ketipov}

\date{10-14.VI.2019}

\institute[IICT-BAS, LSSC'19] {
	Institute of Information and Communication Technologies \\ 
	Bulgarian Academy of Sciences \\
	\medskip
	\textit{todorb@iinf.bas.bg}
}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Overview}
\tableofcontents
\end{frame}

\section{Introduction}

\begin{frame}
\center \huge{Introduction}
\end{frame}

%\begin{frame}
%\frametitle{Clustering}
%\begin{itemize}
%  \item Separation of the data set in set of groups
%  \item Straight clustering - each data sample belongs exactly to only one group
%  \item Fuzzy clustering - each data sample has varying degree of membership to different groups
%\end{itemize}
%Optimal clustering is data set separation which minimizes the distance inside the cluster and maximizes the distance between the clusters
%\end{frame}
%
%\begin{frame}
%\frametitle{Self-Organizing Maps}
%\begin{itemize}
%  \item Proposed by Teuvo Kohonen in the 1980s
%  \item Have application in meteorology, oceanography, project prioritization and selection, seismic facies analysis for oil and gas exploration, failure mode and effects analysis, creation of artwork and many other areas
%  \item They are very useful for visualization by data dimensions reduction
%\end{itemize}
%\end{frame}
%
%\begin{frame}
%\frametitle{SOM in General}
%\begin{itemize}
%  \item Unsupervised competitive learning is used
%  \item Classify input data in predefined number of clusters
%  \item When the net has fewer nodes it achieve results similar to K-means clustering
%\end{itemize}
%\end{frame}
%
%\section{Neighborhood Function Proposition}
%
%\begin{frame}
%\center \huge{Neighborhood Function Proposition}
%\end{frame}
%
%\begin{frame}
%\frametitle{SOM Training}
%\begin{itemize}
%  \item The network consists of a grid with units
%  \item The units are connected to adjacent units with a neighborhood relation
%  \item The network forms an elastic mesh
%  \item Data samples lying near each other in the input space are mapped into nearby grid units
%\end{itemize}
%\end{frame}
%
%\begin{frame}
%\frametitle{Neighborhood Function}
%\begin{itemize}
%  \item It gives scaling factor for the distance between one neuron and other neurons in each step
%  \item The simplest form of a neighborhood function gives 1 for the closest nodes and 0 for all other
%  \item The most used neighborhood function is a Gaussian function
%\end{itemize}
%\end{frame}
%
%\begin{frame}
%\frametitle{Fading Cosine}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=0.45\linewidth]{fig01a}
%\label{fig01a}
%\end{figure}
%\begin{equation} \label{equ01}
%f(x) = 
%	\begin{cases} 
%		cos(x) & -\pi/2 < x < \pi/2 \\
%		\frac{cos(x)}{|x|} & +\pi/2 \geq x \leq -\pi/2 \\
%	\end{cases}
%\end{equation}
%\end{frame}
%
%\begin{frame}
%\frametitle{Exponential Regulated Cosine}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=0.45\linewidth]{fig01b}
%\label{fig01b}
%\end{figure}
%\begin{equation} \label{equ02}
%f(x) = \frac{cos(x)}{e^{|x|}}
%\end{equation}
%\end{frame}
%
%\section{Experiments and Results}
%
%\begin{frame}
%\center \huge{Experiments and Results}
%\end{frame}
%
%\begin{frame}
%\frametitle{Experimental Setup}
%\begin{itemize}
%  \item All experiments are done in C as a programming language
%  \item Single processor desktop machine - Intel Core i5, 2.3 GHz, 2 Cores, 8GB RAM and Mac OS X 10.13.6, Apple LLVM version 9.1.0
%  \item The source code is available at: 
%  http://github.com/Coding-Sunday-Sofia/Kohonen
%\end{itemize}
%\end{frame}
%
%\begin{frame}
%\frametitle{Experimental Data}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=0.9\textwidth]{fig03}
%  \label{fig03}
%\end{figure}
%Rents and living area data set
%\end{frame}
%
%\begin{frame}
%\frametitle{Gausssian Test}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02a}
%  \label{fig02a}
%\end{figure}
%\end{frame}
%
%\begin{frame}
%\frametitle{Fading Cosine Test}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02b}
%  \label{fig02b}
%\end{figure}
%\end{frame}
%
%\begin{frame}
%\frametitle{Exponential Regulated Cosine Test}
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02c}
%  \label{fig02c}
%\end{figure}
%\end{frame}

\section{Conclusions}

\begin{frame}
\center \huge{Conclusions}
\end{frame}

\begin{frame}
\frametitle{Concluding Remarks}
\begin{itemize}
  \item Addition of Hausdorff distance component improves the performance of the genetic algorithm
  \item Calculation of the Hausdorff distance is a little bit slower than the calculation of the Euclidean distance
  \item Better solution fitness estimation generally leads to genetic algorithm convergence improvement
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Questions and Answers}
\center \huge{Thank you for the attention!}
\end{frame}

\end{document}

### 2019-06-01 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/presentation.tex
Few more slides were added.

@@
 
-%\begin{frame}
-%\frametitle{Clustering}
-%\begin{itemize}
-%  \item Separation of the data set in set of groups
-%  \item Straight clustering - each data sample belongs exactly to only one group
-%  \item Fuzzy clustering - each data sample has varying degree of membership to different groups
-%\end{itemize}
-%Optimal clustering is data set separation which minimizes the distance inside the cluster and maximizes the distance between the clusters
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{Self-Organizing Maps}
-%\begin{itemize}
-%  \item Proposed by Teuvo Kohonen in the 1980s
-%  \item Have application in meteorology, oceanography, project prioritization and selection, seismic facies analysis for oil and gas exploration, failure mode and effects analysis, creation of artwork and many other areas
-%  \item They are very useful for visualization by data dimensions reduction
-%\end{itemize}
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{SOM in General}
-%\begin{itemize}
-%  \item Unsupervised competitive learning is used
-%  \item Classify input data in predefined number of clusters
-%  \item When the net has fewer nodes it achieve results similar to K-means clustering
-%\end{itemize}
-%\end{frame}
-%
-%\section{Neighborhood Function Proposition}
-%
-%\begin{frame}
-%\center \huge{Neighborhood Function Proposition}
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{SOM Training}
-%\begin{itemize}
-%  \item The network consists of a grid with units
-%  \item The units are connected to adjacent units with a neighborhood relation
-%  \item The network forms an elastic mesh
-%  \item Data samples lying near each other in the input space are mapped into nearby grid units
-%\end{itemize}
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{Neighborhood Function}
-%\begin{itemize}
-%  \item It gives scaling factor for the distance between one neuron and other neurons in each step
-%  \item The simplest form of a neighborhood function gives 1 for the closest nodes and 0 for all other
-%  \item The most used neighborhood function is a Gaussian function
-%\end{itemize}
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{Fading Cosine}
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=0.45\linewidth]{fig01a}
-%\label{fig01a}
-%\end{figure}
-%\begin{equation} \label{equ01}
-%f(x) = 
-%	\begin{cases} 
-%		cos(x) & -\pi/2 < x < \pi/2 \\
-%		\frac{cos(x)}{|x|} & +\pi/2 \geq x \leq -\pi/2 \\
-%	\end{cases}
-%\end{equation}
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{Exponential Regulated Cosine}
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=0.45\linewidth]{fig01b}
-%\label{fig01b}
-%\end{figure}
-%\begin{equation} \label{equ02}
-%f(x) = \frac{cos(x)}{e^{|x|}}
-%\end{equation}
-%\end{frame}
-%
-%\section{Experiments and Results}
-%
-%\begin{frame}
-%\center \huge{Experiments and Results}
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{Experimental Setup}
-%\begin{itemize}
-%  \item All experiments are done in C as a programming language
-%  \item Single processor desktop machine - Intel Core i5, 2.3 GHz, 2 Cores, 8GB RAM and Mac OS X 10.13.6, Apple LLVM version 9.1.0
-%  \item The source code is available at: 
-%  http://github.com/Coding-Sunday-Sofia/Kohonen
-%\end{itemize}
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{Experimental Data}
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=0.9\textwidth]{fig03}
-%  \label{fig03}
-%\end{figure}
-%Rents and living area data set
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{Gausssian Test}
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02a}
-%  \label{fig02a}
-%\end{figure}
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{Fading Cosine Test}
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02b}
-%  \label{fig02b}
-%\end{figure}
-%\end{frame}
-%
-%\begin{frame}
-%\frametitle{Exponential Regulated Cosine Test}
-%\begin{figure}[h]
-%  \centering
-%  \includegraphics[width=1.0\textwidth,height=0.6\textwidth]{fig02c}
-%  \label{fig02c}
-%\end{figure}
-%\end{frame}
+\begin{frame}
+\frametitle{Rubik's Cube}
+\begin{itemize}
+  \item Invented and introduced by Erno Rubik in the 70s
+  \item The most popular combinatorial puzzle all over the world
+  \item It has 3x3x3 cubical segments
+  \item Six different colors on each subcube square of the exposed sides
+  \item Each of the six planes (3x3x1) can be rotated in 90, 180, 270 or 360 degrees
+  \item As initial state all sides of the cube are in single color
+  \item Scumbling of the puzzle is done by many random rotations
+  \item The goal is to restore the cube in its original state
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Genetic Algorithms}
+\begin{itemize}
+  \item Global optimization strategy
+  \item Inspired by the natural evolution
+  \item Solutions are represented as vectors (individual) of values into the solution space
+  \item Initial population is initialized randomly
+  \item Each new generation is created by selection and recombination
+  \item Suitable for parallel implementation
+\end{itemize}
+\end{frame}
+
+\section{Proposed Rubik's Cube Solver}
+
+\begin{frame}
+\center \huge{Proposed Rubik's Cube Solver}
+\end{frame}
+
+\begin{frame}
+\frametitle{Data Structures}
+\begin{itemize}
+  \item The cube is presented as six (one for each side) two-dimensional (3x3) arrays
+  \item Values in the arrays are integer numbers corresponding to cube's colors
+  \item Six common operations over the cube sides are defined
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Minimal Fully Functional Grammar}
+\begin{itemize}
+  \item T (Top) –90 degrees clockwise rotation of the top side
+  \item L (Left) –90 degrees clockwise rotation of the left side
+  \item B (Back) –90 degrees clockwise rotation of the back side
+  \item R (Right) –90 degrees clockwise rotation of the right side
+  \item F (Front) –90 degrees clockwise rotation of the front side
+  \item D (Down) –90 degrees clockwise rotation of the down side
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Extended Grammars}
+\begin{itemize}
+  \item Counter-clockwise operators included: \\
+  +T, +L, +B, +R, +F, +D, -T, -L, -B, -R, -F, -D
+  \item Number of turns included: \\
+  +1T, +2T, +3T, +1L, +2L, +3L, +1B, +2B, +3B, +1R, +2R, +3R, +1F, +2F, +3F, +1D,+2D, +3D, -1T, -2T, -3T, -1L, -2L, -3L, -1B, -2B, -3B, -1R, -2R, -3R, -1F, -2F, -3F, -1D, -2D, -3D
+\end{itemize}
+\end{frame}
 

### 2019-06-02 Solving-Combinatorial-Puzzles-with-Parallel-Evolutionary-Algorithms/presentation.tex
Full initial version of the presentation was done.

@@
 
+\begin{frame}
+\frametitle{Individuals Representation}
+\begin{itemize}
+  \item Formal grammar sentences with variable length
+  \item Each of the operations can appear at any position many times
+  \item The average expected length of the chromosomes is between 50 and 100
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Recombination Parameters}
+\begin{itemize}
+  \item Single cut point crossover
+  \item Random change of a single instruction mutation
+  \item Random selection of parents
+  \item Elitism rule
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Fitness Value}
+\begin{itemize}
+  \item Instructions from GA individual are applied over the scrambled cube
+  \item Hausdorff distance between manipulated cube and solved cube is calculated
+  \item Lower fitness values are for better individuals
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Proposed Fitness Evaluation}
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=1.0\textwidth,height=0.65\textwidth]{fig01}
+  \label{fig01}
+\end{figure}
+\end{frame}
+
+\section{Experiments and Results}
+
+\begin{frame}
+\center \huge{Experiments and Results}
+\end{frame}
+
+\begin{frame}
+\frametitle{Platform Setup}
+\begin{itemize}
+  \item Intel Core i5, 2.3 GHz, 2 Cores, 8GB RAM
+  \item Mac OS X 10.13.6
+  \item Apple LLVM version 9.1.0 / Open MPI
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Genetic Algorithm Parameters}
+\begin{itemize}
+  \item Generation gap: 0.93
+  \item Crossover rate: 0.98
+  \item Mutation rate: 0.01
+  \item Maximum generations: 10000
+  \item Number of individuals: 37
+  \item Number of variables: floating
+  \item Inserted rate: 100
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Star Topology Results}
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=1.0\textwidth,height=0.5\textwidth]{fig03}
+  \label{fig03}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+\frametitle{Incident Nodes Participation}
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=1.0\textwidth,height=0.5\textwidth]{fig04}
+  \label{fig04}
+\end{figure}
+\end{frame}
+
 \section{Conclusions}
